---
title: "Navigating Pension Investment Risk"
author: "Dylan Berneman"
header-includes:
    - \usepackage{setspace}\doublespacing
output: pdf_document
date: '2023-06-10'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
install.packages("plotrix")
library(plotrix)
library(ggplot2)
library(lubridate)
install.packages("ggrepel")
library(ggrepel)
```
\newpage

# Executive Summary

|   The purpose of this report is to address the important concerns and questions that have been brought up due to the 16.2% investment loss of the MERS fund experienced in calendar year 2022./

|   We will first address the recent rise in long-term bond yields. The rise in long-term bond yields is a result of the significant increase in interest rates from between 0.25% and 0.5% to between 4.25% and 4.5%.  According to CFP,
Hal M. Bundrick, the interest rate is likely to only remain high until the Fed reaches its 2% inflation goal. At that point, the Fed will begin lowering interest rates to restimulate the economy. Since this is projected to occur sometime in 2024, it indicates that the recent rise in long-term bond yields will be temporary effect which will go away in the near future.


Furthermore, the 2022 experience is unlikely to repeat itself once interest rates return to normal. As it is, there was only a *blank percent probability of experiencing a loss of 16% or more.* elaborate on how unusual the 2022 experience was, it has been calculated that the 
\
# The 60/40 Investment Approach
\
|   The first topic that will be addressed is the reason for 2022 investment loss. During 2022, bonds suffered their worst year on record. This is vitally important to note because bonds are considered to be a defensive asset because they are less volatile than stocks. For this reason, investors include bonds in their portfolio as a way to help reduce volatility and overall portfolio risk in the event that there is a significant market downturn, which did occur in 2022. Unexpectedly, the US government increased the interest rate by a cummulative 4.25%, the most since 1980. Consequentially, when interest rates increase, the value of bonds decreases. Additionally, inflation impacts the real rate of return of fixed-income investments. This decrease in real return makes the bond less attractive to investors, leading to a decrease in bond prices. When inflation is larger than the interest rate, investors tend to reinvest their fixed-income investments in order to minimize their total return losses, leading to a decrease in the real value of the fixed-income investments. Because these events took place concurrently alongside a significant market downturn, every single asset allocation strategy resulted in a minimum total loss of 13.3%. 


```{r, warning=FALSE}
library(readxl)

Monthly_Data <- read_excel("Project 2 Historical Data.xlsx", 
    sheet = "60-40 Returns Monthly", range = "B10:D1174")

Monthly_Data1 <- read_excel("Project 2 Historical Data.xlsx", 
    sheet = "60-40 Returns Monthly", range = "B10:D1174")

Data <- read_excel("Project 2 Historical Data.xlsx", 
    sheet = "60-40 Returns Annual", range = "B10:D107")

colnames(Data) = c("Date", "LCTR_true", "FIXED_true")

# 12-month returns
for(i in 1:1153){
  x=1
  data1 = 1
  data2 = 1
  while(x <= 12){
    data1 = data1 * (1 + Monthly_Data$`Large Cap TR`[i+x-1])
    data2 = data2 * (1 + Monthly_Data$FIXED[i+x-1])
    x = x + 1}
  Monthly_Data$`Large Cap TR`[i] = data1 - 1
  Monthly_Data$FIXED[i] = data2 - 1}

Monthly_Data = Monthly_Data[1:1153,]

# 12-month allocation returns
for(i in 0:100){
  alpha = i/100
  Monthly_Data[paste0("LC", i)] = NA
  for(j in 1:1153){
    Monthly_Data[j, length(colnames(Monthly_Data))] = alpha*Monthly_Data$`Large Cap TR`[j]}
  Monthly_Data[paste0("FIX", i)] = NA
  for(j in 1:1153){
    Monthly_Data[j, length(colnames(Monthly_Data))] = (1-alpha)*Monthly_Data$FIXED[j]}
  Monthly_Data[paste0("Folio", i)] = NA
  for(j in 1:1153){
    Monthly_Data[j, length(colnames(Monthly_Data))] = Monthly_Data[j, length(colnames(Monthly_Data))-1] + Monthly_Data[j, length(colnames(Monthly_Data))-2]}}


# monthly allocation returns
for(i in 0:100){
  alpha = i/100
  Monthly_Data1[paste0("LC", i)] = NA
  for(j in 1:1164){
    Monthly_Data1[j, length(colnames(Monthly_Data1))] = alpha*Monthly_Data1$`Large Cap TR`[j]}
  Monthly_Data1[paste0("FIX", i)] = NA
  for(j in 1:1164){
    Monthly_Data1[j, length(colnames(Monthly_Data1))] = (1-alpha)*Monthly_Data1$FIXED[j]}
  Monthly_Data1[paste0("Folio", i)] = NA
  for(j in 1:1164){
    Monthly_Data1[j, length(colnames(Monthly_Data1))] = Monthly_Data1[j, length(colnames(Monthly_Data1))-1] + Monthly_Data1[j, length(colnames(Monthly_Data1))-2]}}

# Annual Allocation returns
for(i in 0:100){
  alpha = i/100
  Data[paste0("LC", i)] = NA
  for(j in 1:97){
    Data[j, length(colnames(Data))] = alpha*Data$LCTR_true[j]}
  Data[paste0("FIX", i)] = NA
  for(j in 1:97){
    Data[j, length(colnames(Data))] = (1-alpha)*Data$FIXED_true[j]}
  Data[paste0("Folio", i)] = NA
  for(j in 1:97){
    Data[j, length(colnames(Data))] = Data[j, length(colnames(Data))-1] + Data[j, length(colnames(Data))-2]}}

# Annual from Monthly
annual = data.frame(matrix(ncol=306,nrow=97))
colnames(annual) = colnames(Monthly_Data)

x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    annual[x,] = Monthly_Data[i,]
    x = x + 1}}

annual$Date = Data$Date
```


```{r}

vect0 = vector()
for(i in 0:100){
  vect0 = append(vect0, paste0("Folio ", i, "/",100-i))
}

vect1 = vector()
vect1 = append(vect1, c(0.02755,
0.029541667,
0.030975,
0.034433333,
0.034825,
0.040783333,
0.041191667,
0.039416667,
0.04055,
0.040733333,
0.041866667,
0.042233333,
0.046941667,
0.049,
0.053458333,
0.061725,
0.067341667,
0.059983333,
0.057966667,
0.069875,
0.079833333,
0.082133333,
0.079441667,
0.07725,
0.085441667,
0.093166667,
0.114333333,
0.135633333,
0.126633333,
0.112558333,
0.124333333,
0.107033333,
0.0769,
0.086091667,
0.089366667,
0.084016667,
0.086191667,
0.08085,
0.07675,
0.065791667))

vect2 = vector()
vect2 = append(vect2, c(-0.007435,
0.003759,
0.029509,
0.028637,
0.017531,
0.017195,
0.013560,
0.006723,
0.013267,
0.016340,
0.009688,
0.019089,
0.034097,
0.029987,
0.046218,
0.060292,
0.054350,
0.032212,
0.033553,
0.083865,
0.116945,
0.067287,
0.047612,
0.065064,
0.086674,
0.125476,
0.118598,
0.085816,
0.037757,
0.037292,
0.038809,
0.037347,
0.010971,
0.043487,
0.043337,
0.045528,
0.059473,
0.030233,
0.028641,
0.027158,
0.026436,
0.025109,
0.032745,
0.016905,
0.016005,
0.026547,
0.033395,
0.015477,
0.023544,
0.018700,
0.032136,
0.033799,
0.025221,
0.040129,
0.001385,
0.026925,
0.014866,
0.029308,
0.017356,
0.014959,
0.007620,
0.007338,
0.020576,
0.020918,
0.018980,
0.022642,
0.013598,
0.068225,
0.062897))

vect2.5 = vect2 + 1

vect3 = vector()
vect4 = vector()
for(i in 1:40){
  x = i
  y = x + 29
  vect3 = append(vect3, mean(vect2[x:y]))
  vect4 = append(vect4, (prod(vect2.5[x:y]))^(1/30)-1)}

geom_vect = vect1 - vect4
arith_vect = vect1 - vect3
```


```{r}
# Mean
Mean = annual[29:97,c(1, seq(6,306,3))]
colnames(Mean)[2:102] = vect0
Mean1 = Mean
Mean1[,2:102] = Mean1[,2:102]+1
Arith = Mean[1:40,]
# arith mean
Arith[, c(2:102)] = NA
# arith sharpe
Arith1 = Arith
# arith risk reward ratio
Arith_rrr = Arith
# geom mean
Geom = Arith
# geom sharpe
Geom1 = Arith
# geom risk reward ratio
Geom_rrr = Arith

# 30 year arith
for(i in 0:100){
  for(j in 1:40){
    x=j
    y=x+29
    Arith[j,i+2] = mean(Mean[x:y, i+2])
    Geom[j,i+2] = (prod(Mean1[x:y, i+2]))^(1/30)-1}}

for(i in 0:100){
  for(j in 1:40){
    x=j
    y=x+29
    std = sqrt(var(Mean[x:y, i+2]))
    Arith_rrr[j, i+2] = std/Arith[j, i+2]
    Arith1[j, i+2] = Arith[j, i+2] - arith_vect[j]
    Arith1[j, i+2] = Arith1[j, i+2]/std
    Geom_rrr[j, i+2] = std/Geom[j, i+2]
    Geom1[j, i+2] = Geom[j, i+2] - geom_vect[j]
    Geom1[j, i+2] = Geom1[j, i+2]/std}}


stats = data.frame(matrix(nrow=101, ncol = 16))
colnames(stats) = c("Allocation", "Spread_num", "Arith_min", "Arith_max", "Arith_Mean", "Arith_STD_DEV", "Arith_Variance", "Arith_Sharpe", "Arith_RRR", "Geom_min", "Geom_max", "Geom_Mean", "Geom_STD_DEV", "Geom_Variance", "Geom_Sharpe", "Geom_RRR")
stats$Allocation = colnames(Mean)[2:102]
stats$Spread_num = c(seq(0,100,1))


# Stats
for(i in 0:100){
    stats[i+1, 3] = min(Arith[, i+2])
    stats[i+1, 4] = max(Arith[, i+2])
    stats[i+1, 5] = sum(Arith[,i+2])
    stats[i+1, 5] = stats[i+1, 5]/40
    stats[i+1, 6] = sqrt(var(Arith[, i+2]))
    stats[i+1, 7] = var(Arith[, i+2])
    stats[i+1, 8] = sum(Arith1[,i+2])
    stats[i+1, 8] = stats[i+1, 8]/40
    stats[i+1, 9] = sum(Arith_rrr[,i+2])
    stats[i+1, 9] = stats[i+1, 9]/40
    stats[i+1, 10] = min(Geom[, i+2])
    stats[i+1, 11] = max(Geom[, i+2])
    stats[i+1, 12] = sum(Geom[,i+2])
    stats[i+1, 12] = stats[i+1, 12]/40
    stats[i+1, 13] = sqrt(var(Geom[, i+2]))
    stats[i+1, 14] = var(Geom[, i+2])
    stats[i+1, 15] = sum(Geom1[,i+2])
    stats[i+1, 15] = stats[i+1, 15]/40
    stats[i+1, 16] = sum(Geom_rrr[,i+2])
    stats[i+1, 16] = stats[i+1, 16]/40}

# Arith 30-yr average vs std
signif_pts0 = stats[c(1, 61, 70, 101),]
ggplot(data = stats, aes(x = Arith_STD_DEV, y = Arith_Mean)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x=Arith_STD_DEV, y=Arith_Mean, 
                                   label = paste0("mean: ", round(Arith_Mean,4), "\n", "sd: ", round(Arith_STD_DEV,4))),
             color = "green", size=4, nudge_x = .0002, nudge_y = 0.0001) +
  geom_point(data=signif_pts0[1,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "red", size = 5) +
  geom_point(data=signif_pts0[2,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "yellow", size = 5) +
  geom_point(data=signif_pts0[3,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "green", size = 5) +
  geom_point(data=signif_pts0[4,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "orange", size = 5) +
  geom_point(data=signif_pts0[5,], aes(x=Arith_STD_DEV, y=Arith_Mean, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "red", "60/40" = "yellow", "69/31" = "green", "100/0" = "orange"),
                     labels = c("0/100", "60/40", "69/31", "100/0"))+
  labs(title = "Arithmetic 30-Year Returns") +
  ylab("Average") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr arithmetic sharpe ratio
signif_pts1 = stats[c(1, 31, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Arith_Sharpe)) + 
  geom_point() + 
  geom_label(data=signif_pts1[2,], aes(x = Spread_num, y = Arith_Sharpe, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "Sharpe Ratio: ", round(Arith_Sharpe, 4))),
             color = "green", size=4, nudge_y = -.025) + 
  geom_point(data=signif_pts1, aes(x = Spread_num, y = Arith_Sharpe), color = "red", size = 4) +
  labs(title = "Arithmetic 30-Year Sharpe Ratio") +
  ylab("Sharpe Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts1[1,], aes(x = Spread_num, y = Arith_Sharpe), color = "orange", size = 5) +
  geom_point(data=signif_pts1[2,], aes(x = Spread_num, y = Arith_Sharpe), color = "green", size = 5) +
  geom_point(data=signif_pts1[3,], aes(x = Spread_num, y = Arith_Sharpe), color = "yellow", size = 5) +
  geom_point(data=signif_pts1[4,], aes(x = Spread_num, y = Arith_Sharpe), color = "red", size = 5) +
  geom_point(data=signif_pts1[5,], aes(x = Spread_num, y = Arith_Sharpe, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "30/70" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "30/70", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr arith risk/reward ratio
signif_pts2 = stats[c(1, 23, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Arith_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts2[2,], aes(x = Spread_num, y = Arith_RRR, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "Risk/Reward: ", round(Arith_RRR, 4))),
             color = "green", size=4, nudge_y = .05) + 
  labs(title = "Arithmetic 30-Year Risk/Reward Ratio") +
  ylab("Risk/Reward Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts2[1,], aes(x = Spread_num, y = Arith_RRR), color = "orange", size = 5) +
  geom_point(data=signif_pts2[2,], aes(x = Spread_num, y = Arith_RRR), color = "green", size = 5) +
  geom_point(data=signif_pts2[3,], aes(x = Spread_num, y = Arith_RRR), color = "yellow", size = 5) +
  geom_point(data=signif_pts2[4,], aes(x = Spread_num, y = Arith_RRR), color = "red", size = 5) +
  geom_point(data=signif_pts2[5,], aes(x = Spread_num, y = Arith_RRR, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "22/78" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "22/78", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.85, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# Geom 30-yr average vs std
signif_pts3 = stats[c(1, 59, 61, 101),]
ggplot(data = stats, aes(x = Geom_STD_DEV, y = Geom_Mean)) + 
  geom_point() + 
  geom_label(data=signif_pts3[2,], aes(x=Geom_STD_DEV, y=Geom_Mean, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "mean: ", round(Geom_Mean, 4), "\n", 
                                                  "sd: ", round(Geom_STD_DEV, 4))), 
             color = "green", size=4, nudge_x = .0002) + 
  labs(title = "Geometric 30-Year Returns") +
  ylab("Average") +
  xlab("Standard Deviation") +
  geom_point(data=signif_pts3[1,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "red", size = 5) +
  geom_point(data=signif_pts3[2,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "green", size = 5) +
  geom_point(data=signif_pts3[3,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "yellow", size = 5) +
  geom_point(data=signif_pts3[4,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "orange", size = 5) +
  geom_point(data=signif_pts3[5,], aes(x=Geom_STD_DEV, y=Geom_Mean, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "red", "58/42" = "green", "60/40" = "yellow", "100/0" = "orange"),
                     labels = c("0/100", "58/42", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr arithmetic sharpe ratio 
signif_pts4 = stats[c(1, 30, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Geom_Sharpe)) + 
  geom_point() + 
  geom_label(data=signif_pts4[2,], aes(x = Spread_num, y = Geom_Sharpe, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "Sharpe Ratio: ", round(Geom_Sharpe, 4))),
             color = "green", size=4, nudge_y = -.025) + 
  labs(title = "Geometric 30-Year Sharpe Ratio") +
  ylab("Sharpe Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts4[1,], aes(x = Spread_num, y = Geom_Sharpe), color = "orange", size = 5) +
  geom_point(data=signif_pts4[2,], aes(x = Spread_num, y = Geom_Sharpe), color = "green", size = 5) +
  geom_point(data=signif_pts4[3,], aes(x = Spread_num, y = Geom_Sharpe), color = "yellow", size = 5) +
  geom_point(data=signif_pts4[4,], aes(x = Spread_num, y = Geom_Sharpe), color = "red", size = 5) +
  geom_point(data=signif_pts4[5,], aes(x = Spread_num, y = Geom_Sharpe, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "29/71" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "29/71", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr geometric risk/reward ratio 
signif_pts5 = stats[c(1, 23, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Geom_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts5[2,], aes(x = Spread_num, y = Geom_RRR, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", "Risk/Reward: ", round(Geom_RRR, 4))),
             color = "green", size=4, nudge_y = .1) + 
  geom_point(data=signif_pts5, aes(x = Spread_num, y = Geom_RRR), color = "red", size = 4) +
  labs(title = "Geometric 30-Year Risk/Reward Ratio") +
  ylab("Risk/Reward Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts5[1,], aes(x = Spread_num, y = Geom_RRR), color = "orange", size = 5) +
  geom_point(data=signif_pts5[2,], aes(x = Spread_num, y = Geom_RRR), color = "green", size = 5) +
  geom_point(data=signif_pts5[3,], aes(x = Spread_num, y = Geom_RRR), color = "yellow", size = 5) +
  geom_point(data=signif_pts5[4,], aes(x = Spread_num, y = Geom_RRR), color = "red", size = 5) +
  geom_point(data=signif_pts5[5,], aes(x = Spread_num, y = Geom_RRR, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "22/78" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "22/78", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.85, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))
```


```{r}
Inflate_Bill <- read_excel("Project 2 Historical Data.xlsx", 
    range = "AO11:AR1175", col_types = c("numeric", 
        "skip", "skip", "numeric")) 
Inflate_Bill["Date"] = NA
Inflate_Bill$Date = Monthly_Data1$Date
Inflate_Bill = Inflate_Bill[,c(3,1:2)]

Inflate_Bill_1a = Inflate_Bill
Inflate_Bill_1g = Inflate_Bill
Inflate_Bill_1g[,2:3] = 1 + Inflate_Bill_1g[,2:3]
Inflate_Bill_a = Inflate_Bill_1a
Inflate_Bill_a[,2:3] = NA
Inflate_Bill_g = Inflate_Bill_1g
Inflate_Bill_g[,2:3] = NA

for(j in 2:3){
  for(i in 1:1153){
    x=i
    y=i+11
    Inflate_Bill_g[i,j] = prod(Inflate_Bill_1g[x:y, j])^(1/12)-1
    Inflate_Bill_a[i,j] = sum(Inflate_Bill_1a[x:y, j])/12}}
Inflate_Bill_g = Inflate_Bill_g[1:1153,]
Inflate_Bill_a = Inflate_Bill_a[1:1153,]

Inflate_Bill_g["diff"] = Inflate_Bill_g$`Ibbotson® SBBI® US (30-Day) Treasury Bills`-Inflate_Bill_g$`Ibbotson® SBBI® US Inflation`
Inflate_Bill_a["diff"] = Inflate_Bill_a$`Ibbotson® SBBI® US (30-Day) Treasury Bills`-Inflate_Bill_a$`Ibbotson® SBBI® US Inflation`


Monthly_Data1a = Monthly_Data1[, c(1, seq(6,306,3))]
Monthly_Data1g = Monthly_Data1a
Monthly_Data1g[,2:102] = 1 + Monthly_Data1g[,2:102]
Monthly_Data_a = Monthly_Data1a
Monthly_Data_a[,2:102] = NA
Monthly_Data_a_sd = Monthly_Data_a
Monthly_Data_g = Monthly_Data1g
Monthly_Data_g[,2:102] = NA
Monthly_Data_g_sd = Monthly_Data_g
Sharpe_a = Monthly_Data_a
Sharpe_g = Monthly_Data_g
RRR_a = Monthly_Data_a
RRR_g = Monthly_Data_g

for(i in 2:102){
  for(j in 1:1153){
    x=j
    y=x+11
    Monthly_Data_a[j,i] = sum(Monthly_Data1a[x:y, i])/12
    sqrt_a = sqrt(var(Monthly_Data1a[x:y, i]))
    Sharpe_a[j,i] = Monthly_Data_a[j,i] - Inflate_Bill_a$diff[j]
    Sharpe_a[j,i] = Sharpe_a[j,i]/sqrt_a
    RRR_a[j,i] = sqrt_a / Monthly_Data_a[j,i]
    
    Monthly_Data_g[j,i] = prod(Monthly_Data1g[x:y, i])^(1/12) - 1
    sqrt_g = sqrt(var(Monthly_Data1g[x:y, i]))
    Sharpe_g[j,i] = Monthly_Data_g[j,i] - Inflate_Bill_g$diff[j]
    Sharpe_g[j,i] = Sharpe_g[j,i]/sqrt_g
    RRR_g[j,i] = sqrt_a / Monthly_Data_g[j,i]}}

Monthly_Data_a = Monthly_Data_a[1:1153,]
Monthly_Data_g = Monthly_Data_g[1:1153,]
Sharpe_a = Sharpe_a[1:1153,]
Sharpe_g = Sharpe_g[1:1153,]
RRR_a = RRR_a[1:1153,]
RRR_a[,2:102] = abs(RRR_a[,2:102])
RRR_g = RRR_g[1:1153,]
RRR_g[,2:102] = abs(RRR_g[,2:102])

# annual monthly_a
Yearly_Monthly_Data_a = data.frame(matrix(ncol=102,nrow=97))
colnames(Yearly_Monthly_Data_a) = colnames(Monthly_Data_a)
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    Yearly_Monthly_Data_a[x,] = Monthly_Data_a[i,]
    x = x + 1}}
Yearly_Monthly_Data_a$Date = Data$Date

# annual monthly_g
Yearly_Monthly_Data_g = data.frame(matrix(ncol=102,nrow=97))
colnames(Yearly_Monthly_Data_g) = colnames(Monthly_Data_g)
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    Yearly_Monthly_Data_g[x,] = Monthly_Data_g[i,]
    x = x + 1}}
Yearly_Monthly_Data_g$Date = Data$Date

# annual Sharpe_a
Yearly_Sharpe_a = data.frame(matrix(ncol=102,nrow=97))
colnames(Yearly_Sharpe_a) = colnames(Sharpe_a)
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    Yearly_Sharpe_a[x,] = Sharpe_a[i,]
    x = x + 1}}
Yearly_Sharpe_a$Date = Data$Date

# annual Sharpe_g
Yearly_Sharpe_g = data.frame(matrix(ncol=102,nrow=97))
colnames(Yearly_Sharpe_g) = colnames(Sharpe_g)
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    Yearly_Sharpe_g[x,] = Sharpe_g[i,]
    x = x + 1}}
Yearly_Sharpe_g$Date = Data$Date

# annual RRR_a
Yearly_RRR_a = data.frame(matrix(ncol=102,nrow=97))
colnames(Yearly_RRR_a) = colnames(RRR_a)
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    Yearly_RRR_a[x,] = RRR_a[i,]
    x = x + 1}}
Yearly_RRR_a$Date = Data$Date

# annual RRR_g
Yearly_RRR_g = data.frame(matrix(ncol=102,nrow=97))
colnames(Yearly_RRR_g) = colnames(RRR_g)
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    Yearly_RRR_g[x,] = RRR_g[i,]
    x = x + 1}}
Yearly_RRR_g$Date = Data$Date



stats1 = data.frame(matrix(nrow=101, ncol = 10))
colnames(stats1) = c("Allocation", "Spread_num", "Mean_a", "STD_DEV_a", "Sharpe_a", "RRR_a", "Mean_g", "STD_DEV_g", "Sharpe_g", "RRR_g")
stats1$Allocation = colnames(Mean)[2:102]
stats1$Spread_num = c(seq(0,100,1))

# Stats
for(i in 0:100){
  stats1$Mean_a[i+1] = sum(Monthly_Data_a[,i+2])/1153
  stats1$STD_DEV_a[i+1] = sqrt(var(Monthly_Data_a[,i+2]))
  stats1$Sharpe_a[i+1] = sum(Sharpe_a[,i+2])/1153
  stats1$RRR_a[i+1] = stats1$STD_DEV_a[i+1] / stats1$Mean_a[i+1]
  stats1$Mean_g[i+1] = sum(Monthly_Data_g[,i+2])/1153
  stats1$STD_DEV_g[i+1] = sqrt(var(Monthly_Data_g[,i+2]))
  stats1$Sharpe_g[i+1] = sum(Sharpe_g[,i+2])/1153
  stats1$RRR_g[i+1] = stats1$STD_DEV_g[i+1] / stats1$Mean_g[i+1]}
  

stats2 = data.frame(matrix(nrow=101, ncol = 10))
colnames(stats2) = c("Allocation", "Spread_num", "Mean_a", "STD_DEV_a", "Sharpe_a", "RRR_a", "Mean_g", "STD_DEV_g", "Sharpe_g", "RRR_g")
stats2$Allocation = colnames(Mean)[2:102]
stats2$Spread_num = c(seq(0,100,1))

# Stats yearly
for(i in 0:100){
  stats2$Mean_a[i+1] = sum(Yearly_Monthly_Data_a[,i+2])/97
  stats2$STD_DEV_a[i+1] = sqrt(var(Yearly_Monthly_Data_a[,i+2]))
  stats2$Sharpe_a[i+1] = sum(Yearly_Sharpe_a[,i+2])/97
  stats2$RRR_a[i+1] = stats2$STD_DEV_a[i+1] / stats2$Mean_a[i+1]
  stats2$Mean_g[i+1] = sum(Yearly_Monthly_Data_g[,i+2])/97
  stats2$STD_DEV_g[i+1] = sqrt(var(Yearly_Monthly_Data_g[,i+2]))
  stats2$Sharpe_g[i+1] = sum(Yearly_Sharpe_g[,i+2])/97
  stats2$RRR_g[i+1] = stats2$STD_DEV_g[i+1] / stats2$Mean_g[i+1]}

x=sum(Monthly_Data1a[1:12, 2])/12
y=sqrt(var(Monthly_Data1a[1:12, 2]))
y/x

annual_rrr1 = annual[c(1, seq(6,306,3))]
annual_RRR1 = data.frame(matrix(ncol=405, nrow = 68))
vect44 = vector()
for(i in 0:100){
  vect44 = append(vect44, paste0("Risk ", i, "/", 100-i))
  vect44 = append(vect44, paste0("Reward ", i, "/", 100-i))
  vect44 = append(vect44, paste0("Risk-Reward Ratio ", i, "/", 100-i))
  vect44 = append(vect44, paste0("Reward-Risk Ratio ", i, "/", 100-i))}
colnames(annual_RRR1) = c("Date", vect44)
annual_RRR1$Date = Data$Date[1:68]
annual_RRR1[,2:304] = NA

t=2
for(i in 2:102){
  for(j in 1:68){
    x=j
    y=x+29
    risk = 0
    reward = 0
    for(z in x:y){
      if(annual_rrr1[z,i] > 0){
        reward = reward + annual_rrr1[z,i]}
      if(annual_rrr1[z,i] < 0){
        risk = risk + annual_rrr1[z,i]}}
    annual_RRR1[j,t] = risk
    annual_RRR1[j,t+1] = reward
    annual_RRR1[j,t+2] = abs(risk/reward)
    annual_RRR1[j,t+3] = abs(reward/risk)}
    t=t+4}

stats3 = data.frame(matrix(nrow=101, ncol = 6))
colnames(stats3) = c("Allocation", "Spread_num", "min", "max", "Mean", "STD_DEV")
stats3$Allocation = colnames(Mean)[2:102]
stats3$Spread_num = c(seq(0,100,1))


for(i in 0:100){
    stats3[i+1, 3] = min(annual_RRR1[, i+2])
    stats3[i+1, 4] = max(annual_RRR1[, i+2])
    stats3[i+1, 5] = sum(annual_RRR1[, i+2])/68
    stats3[i+1, 6] = sqrt(var(annual_RRR1[, i+2]))}


annual_rrr = annual[c(1, seq(6,306,3))]
annual_RRR = data.frame(matrix(ncol=6, nrow = 101))
colnames(annual_RRR) = c("Allocation", "Num", "Risk", "Reward", "Risk-Reward Ratio", "Reward-Risk Ratio")
annual_RRR$Allocation = colnames(annual_rrr)[2:102]
annual_RRR$Num = c(0:100)
for(i in 0:100){
  minus = 0
  plus = 0
  for(j in 1:97){
    if(annual_rrr[j,i+2] > 0){
      plus = plus + annual_rrr[j,i+2]}
    if(annual_rrr[j,i+2] < 0){
      minus = minus + annual_rrr[j,i+2]}}
  annual_RRR$Risk[i+1] = minus
  annual_RRR$Reward[i+1] = plus
  annual_RRR$`Risk-Reward Ratio`[i+1] = abs(minus/plus)
  annual_RRR$`Reward-Risk Ratio`[i+1] = abs(plus/minus)}

stats3 = data.frame(matrix(nrow=101, ncol = 6))
colnames(stats3) = c("Allocation", "Spread_num", "min", "max", "Mean", "STD_DEV")
stats3$Allocation = colnames(Mean)[2:102]
stats3$Spread_num = c(seq(0,100,1))


for(i in 0:100){
    stats3[i+1, 3] = min(annual_RRR[, i+2])
    stats3[i+1, 4] = max(annual_RRR[, i+2])
    stats3[i+1, 5] = sum(annual_RRR[, i+2])/68
    stats3[i+1, 6] = sqrt(var(annual_RRR[, i+2]))}

```

```{r}

# Arith 30-yr average vs std
signif_pts0 = stats[c(1, 61, 70, 101),]
ggplot(data = stats, aes(x = Arith_STD_DEV, y = Arith_Mean)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x=Arith_STD_DEV, y=Arith_Mean, 
                                   label = paste0("mean: ", round(Arith_Mean,4), "\n", "sd: ", round(Arith_STD_DEV,4))),
             color = "green", size=4, nudge_x = .0002, nudge_y = 0.0001) +
  geom_point(data=signif_pts0[1,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "red", size = 5) +
  geom_point(data=signif_pts0[2,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "yellow", size = 5) +
  geom_point(data=signif_pts0[3,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "green", size = 5) +
  geom_point(data=signif_pts0[4,], aes(x=Arith_STD_DEV, y=Arith_Mean), color = "orange", size = 5) +
  geom_point(data=signif_pts0[5,], aes(x=Arith_STD_DEV, y=Arith_Mean, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "red", "60/40" = "yellow", "69/31" = "green", "100/0" = "orange"),
                     labels = c("0/100", "60/40", "69/31", "100/0"))+
  labs(title = "Arithmetic 30-Year Returns") +
  ylab("Average") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr arithmetic sharpe ratio
signif_pts1 = stats[c(1, 31, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Arith_Sharpe)) + 
  geom_point() + 
  geom_label(data=signif_pts1[2,], aes(x = Spread_num, y = Arith_Sharpe, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "Sharpe Ratio: ", round(Arith_Sharpe, 4))),
             color = "green", size=4, nudge_y = -.025) + 
  geom_point(data=signif_pts1, aes(x = Spread_num, y = Arith_Sharpe), color = "red", size = 4) +
  labs(title = "Arithmetic 30-Year Sharpe Ratio") +
  ylab("Sharpe Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts1[1,], aes(x = Spread_num, y = Arith_Sharpe), color = "orange", size = 5) +
  geom_point(data=signif_pts1[2,], aes(x = Spread_num, y = Arith_Sharpe), color = "green", size = 5) +
  geom_point(data=signif_pts1[3,], aes(x = Spread_num, y = Arith_Sharpe), color = "yellow", size = 5) +
  geom_point(data=signif_pts1[4,], aes(x = Spread_num, y = Arith_Sharpe), color = "red", size = 5) +
  geom_point(data=signif_pts1[5,], aes(x = Spread_num, y = Arith_Sharpe, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "30/70" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "30/70", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr arith risk/reward ratio
signif_pts2 = stats[c(1, 23, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Arith_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts2[2,], aes(x = Spread_num, y = Arith_RRR, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "Risk/Reward: ", round(Arith_RRR, 4))),
             color = "green", size=4, nudge_y = .05) + 
  labs(title = "Arithmetic 30-Year Risk/Reward Ratio") +
  ylab("Risk/Reward Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts2[1,], aes(x = Spread_num, y = Arith_RRR), color = "orange", size = 5) +
  geom_point(data=signif_pts2[2,], aes(x = Spread_num, y = Arith_RRR), color = "green", size = 5) +
  geom_point(data=signif_pts2[3,], aes(x = Spread_num, y = Arith_RRR), color = "yellow", size = 5) +
  geom_point(data=signif_pts2[4,], aes(x = Spread_num, y = Arith_RRR), color = "red", size = 5) +
  geom_point(data=signif_pts2[5,], aes(x = Spread_num, y = Arith_RRR, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "22/78" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "22/78", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.85, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# Geom 30-yr average vs std
signif_pts3 = stats[c(1, 59, 61, 101),]
ggplot(data = stats, aes(x = Geom_STD_DEV, y = Geom_Mean)) + 
  geom_point() + 
  geom_label(data=signif_pts3[2,], aes(x=Geom_STD_DEV, y=Geom_Mean, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "mean: ", round(Geom_Mean, 4), "\n", 
                                                  "sd: ", round(Geom_STD_DEV, 4))), 
             color = "green", size=4, nudge_x = .0002) + 
  labs(title = "Geometric 30-Year Returns") +
  ylab("Average") +
  xlab("Standard Deviation") +
  geom_point(data=signif_pts3[1,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "red", size = 5) +
  geom_point(data=signif_pts3[2,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "green", size = 5) +
  geom_point(data=signif_pts3[3,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "yellow", size = 5) +
  geom_point(data=signif_pts3[4,], aes(x=Geom_STD_DEV, y=Geom_Mean), color = "orange", size = 5) +
  geom_point(data=signif_pts3[5,], aes(x=Geom_STD_DEV, y=Geom_Mean, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "red", "58/42" = "green", "60/40" = "yellow", "100/0" = "orange"),
                     labels = c("0/100", "58/42", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr arithmetic sharpe ratio 
signif_pts4 = stats[c(1, 30, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Geom_Sharpe)) + 
  geom_point() + 
  geom_label(data=signif_pts4[2,], aes(x = Spread_num, y = Geom_Sharpe, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", 
                                                  "Sharpe Ratio: ", round(Geom_Sharpe, 4))),
             color = "green", size=4, nudge_y = -.025) + 
  labs(title = "Geometric 30-Year Sharpe Ratio") +
  ylab("Sharpe Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts4[1,], aes(x = Spread_num, y = Geom_Sharpe), color = "orange", size = 5) +
  geom_point(data=signif_pts4[2,], aes(x = Spread_num, y = Geom_Sharpe), color = "green", size = 5) +
  geom_point(data=signif_pts4[3,], aes(x = Spread_num, y = Geom_Sharpe), color = "yellow", size = 5) +
  geom_point(data=signif_pts4[4,], aes(x = Spread_num, y = Geom_Sharpe), color = "red", size = 5) +
  geom_point(data=signif_pts4[5,], aes(x = Spread_num, y = Geom_Sharpe, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "29/71" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "29/71", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))


# 30 yr geometric risk/reward ratio 
signif_pts5 = stats[c(1, 23, 61, 101),]
ggplot(data = stats, aes(x = Spread_num, y = Geom_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts5[2,], aes(x = Spread_num, y = Geom_RRR, 
                                   label = paste0(Spread_num, "/", 100-Spread_num, "\n", "Risk/Reward: ", round(Geom_RRR, 4))),
             color = "green", size=4, nudge_y = .1) + 
  geom_point(data=signif_pts5, aes(x = Spread_num, y = Geom_RRR), color = "red", size = 4) +
  labs(title = "Geometric 30-Year Risk/Reward Ratio") +
  ylab("Risk/Reward Ratio") +
  xlab("Allocation (Large Cap)") +
  geom_point(data=signif_pts5[1,], aes(x = Spread_num, y = Geom_RRR), color = "orange", size = 5) +
  geom_point(data=signif_pts5[2,], aes(x = Spread_num, y = Geom_RRR), color = "green", size = 5) +
  geom_point(data=signif_pts5[3,], aes(x = Spread_num, y = Geom_RRR), color = "yellow", size = 5) +
  geom_point(data=signif_pts5[4,], aes(x = Spread_num, y = Geom_RRR), color = "red", size = 5) +
  geom_point(data=signif_pts5[5,], aes(x = Spread_num, y = Geom_RRR, color = Allocation), size = 5) + 
  scale_color_manual(values = c("0/100" = "orange", "22/78" = "green", "60/40" = "yellow", "100/0" = "red"),
                     labels = c("0/100", "22/78", "60/40", "100/0"))+
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.85, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15),
        legend.background = element_rect(fill="gray90", size=.5))

```

```{r}
# 12 month average




# Mean
Mean2 = Monthly_Data1[1:1164,c(1, seq(6,306,3))]
colnames(Mean2)[2:102] = vect0
# Sharpe
Sharpe = Mean2
Sharpe[,2:102] = NA

for(i in 0:100){
  for(j in 1:1164){
    Sharpe[j, i+2] = Mean2[j, i+2] - Inflate_Bill$diff[j]}}

stats1 = data.frame(matrix(nrow=101, ncol = 9))
colnames(stats1) = c("Allocation", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance", "Sharpe", "RRR")
stats1$Allocation = colnames(Mean)[2:102]
stats1$Spread_num = c(seq(0,100,1))


# Stats
for(i in 0:100){
  stats1$Sharpe[i+1] = sum(Sharpe[,i+2])/1164
  stats1$Sharpe[i+1] = stats1$Sharpe[i+1]/sqrt(var(Mean[, i+2]))
  stats1[i+1, 3] = min(Mean2[, i+2])
  stats1[i+1, 4] = max(Mean2[, i+2])
  stats1[i+1, 5] = sum(Mean2[,i+2])
  stats1[i+1, 5] = stats1[i+1, 5]/1164
  stats1[i+1, 6] = sqrt(var(Mean2[, i+2]))
  stats1[i+1, 7] = var(Mean2[, i+2])
  stats1[i+1, 9] = stats1$STD_DEV[i+1]/stats1$Mean[i+1]}

```

```{r}
# geometric
Geometric = annual[,c(1, seq(6,306,3))]
colnames(Geometric)[2:102] = vect0

Geometric1 = Geometric
Geometric1[,2:102] = 1+Geometric1[,2:102]

Geometric2 = Geometric1[1:68,]
Geometric2[, c(2:102)] = NA
# 30 year geom
for(i in 0:100){
  for(j in 1:68){
    x=j
    y=x+29
    Geometric2[j, i+2] = prod(Geometric1[x:y, i+2])
    Geometric2[j, i+2] = Geometric2[j, i+2]^(1/30) - 1}}

Geometric_stats = data.frame(matrix(nrow=101, ncol = 7))
colnames(Geometric_stats) = c("Allocation", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance")
Geometric_stats$Allocation = colnames(Geometric2)[2:102]
Geometric_stats$Spread_num = c(seq(0,100,1))


# Geometric Stats
for(i in 0:100){
    Geometric_stats[i+1, 3] = min(Geometric2[, i+2])
    Geometric_stats[i+1, 4] = max(Geometric2[, i+2])
    Geometric_stats[i+1, 5] = sum(Geometric2[,i+2])
    Geometric_stats[i+1, 5] = Geometric_stats[i+1, 5]/68
    Geometric_stats[i+1, 6] = sqrt(var(Geometric2[, i+2]))
    Geometric_stats[i+1, 7] = var(Geometric2[, i+2])}

# 30 yr geom avg v std
signif_pts = Geometric_stats[c(1, 61, 78, 101),]
ggplot(data = Geometric_stats, aes(x = STD_DEV, y = Mean)) + geom_point() + geom_label(data=signif_pts, aes(x=STD_DEV, y=Mean, label = paste0(Spread_num, "/", 100-Spread_num)), color = "red", size=7, nudge_x = -.001) + 
  geom_point(data=signif_pts, aes(x=STD_DEV, y=Mean), color = "red", size = 4) +
  labs(title = "30 Year Geometric Returns") +
  ylab("Average") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15))


# 3 yr geom
Geometric3 = Geometric1[1:95,]
Geometric3[, c(2:102)] = NA
# 3 year geom
for(i in 0:100){
  for(j in 1:95){
    x=j
    y=x+2
    Geometric3[j, i+2] = prod(Geometric1[x:y, i+2])
    Geometric3[j, i+2] = Geometric3[j, i+2]^(1/3) - 1}}

Geometric_stats2 = data.frame(matrix(nrow=101, ncol = 7))
colnames(Geometric_stats2) = c("Allocation", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance")
Geometric_stats2$Allocation = colnames(Geometric3)[2:102]
Geometric_stats2$Spread_num = c(seq(0,100,1))

# Geometric Stats
for(i in 0:100){
    Geometric_stats2[i+1, 3] = min(Geometric3[, i+2])
    Geometric_stats2[i+1, 4] = max(Geometric3[, i+2])
    Geometric_stats2[i+1, 5] = sum(Geometric3[,i+2])
    Geometric_stats2[i+1, 5] = Geometric_stats2[i+1, 5]/95
    Geometric_stats2[i+1, 6] = sqrt(var(Geometric3[, i+2]))
    Geometric_stats2[i+1, 7] = var(Geometric3[, i+2])}

Geometric_stats2 = Geometric_stats2 %>%
  mutate("Sharpe Ratio" = Geometric_stats2$Mean / Geometric_stats2$STD_DEV)

# 3 yr geom avg v std
signif_pts2 = Geometric_stats2
ggplot(data = Geometric_stats2, aes(x = STD_DEV, y = Mean)) + geom_point() + geom_label(data=signif_pts2, aes(x=STD_DEV, y=Mean, label = paste0(Spread_num, "/", 100-Spread_num)), color = "red", size=7, nudge_x = -.001) + 
  geom_point(data=signif_pts2, aes(x=STD_DEV, y=Mean), color = "red", size = 4) +
  labs(title = "3 Year Geometric Returns") +
  ylab("Average") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15))






# Geometric 30-yr avg
for(i in 0:100){
  alpha = i/100
  Geometric[vect0[i+1]] <- alpha*Geometric$`Large Cap TR` + (1-alpha)*Geometric$FIXED}


prod(geom_annual0[1:30, 2])^(1/30)-1
geom_annual0 = annual[,c(1, seq(6,306,3))]
geom_annual0[,2:102] = geom_annual0[,2:102] + 1 

geom_annual = geom_annual0[1:68,]
for(i in 2:102){
  for(j in 1:68){
    geom_annual[j, i] = prod(geom_annual0[j:j+29, i])^(1/30) - 1}}

Geometric_stats_annual = data.frame(matrix(nrow=101, ncol = 7))
colnames(Geometric_stats_annual) = c("Allocation", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance")
Geometric_stats_annual$Allocation = colnames(Geometric2)[4:104]
Geometric_stats_annual$Spread_num = c(seq(0,100,1))

for(i in 0:100){
    Geometric_stats_annual[i+1, 3] = min(geom_annual[, i+2])
    Geometric_stats_annual[i+1, 4] = max(geom_annual[, i+2])
    Geometric_stats_annual[i+1, 5] = sum(geom_annual[,i+2])
    Geometric_stats_annual[i+1, 5] = Geometric_stats_annual[i+1, 5]/68
    Geometric_stats_annual[i+1, 6] = sqrt(var(geom_annual[, i+2]))
    Geometric_stats_annual[i+1, 7] = var(geom_annual[, i+2])}


comp = data.frame(matrix(nrow=97, ncol=306))
vect = vector()
vect= append(vect, NA)
for(i in 2:306){
  vect = append(vect, mean(annual[,i]))}

colnames(comp) = colnames(Data)
for(i in 1:306){
  for(j in 1:97){
    if(annual[j,i] == Data[j,i]){
      comp[j,i] = TRUE}
    else{
      comp[j,i] = (annual[j,i] - Data[j,i])^2}}}

for(i in 2:306){
  if(annual[j,i] == Data[j,i]){
      comp[98,i] = 0}
    else{
      comp[98,i] = sqrt((1/97)*sum(comp[1:97,i]) / (vect[i])^2)}}


vect = vector()
vect = append(vect, "Date")
vect = append(vect, "Large Cap")
vect = append(vect, "Fixed")
for(i in 4:306){
  if((i-3)%%3 == 1){
    vect = append(vect, "Large Cap")}
  if((i-3)%%3 == 2){
    vect = append(vect, "Fixed")}
  if((i-3)%%3 == 0){
    vect = append(vect, "Portfolio")}}

data = data.frame(matrix(ncol = 306))
data[1,] = vect
colnames(data) = colnames(Monthly_Data)

list1 = c(1)
for(i in 1:306){
  if(data[1,i] == "Portfolio"){
    list1 = append(list1, i)}}
Monthly_Portfolio = Monthly_Data[, list1]

list2 = c(1)
for(i in 1:306){
  if(data[1,i] == "Large Cap"){
    list2 = append(list2, i)}}
Monthly_LC = Monthly_Data[, list2]

list3 = c(1)
for(i in 1:306){
  if(data[1,i] == "Fixed"){
    list3 = append(list3, i)}}
Monthly_Fixed = Monthly_Data[, list3]


# 60-40 historic returns
Monthly_Data60 = Monthly_Data[c("Date", "LC60", "FIX60", "Folio60")]

Data60 = Monthly_Data60[c(67, 136, 574, 987, 1153), c(1,4)]

ggplot(data = Monthly_Data60, aes(x = Date, y = FIX60,color="Fixed")) + 
  geom_line() +
  geom_line(data = Monthly_Data60, aes(x = Date, y = LC60, color="Large Cap")) +
  geom_line(data = Monthly_Data60, aes(x = Date, y = Folio60, color="Portfolio")) + 
  theme(plot.title = element_text(hjust = 0.5, size =18),
        legend.title = element_blank(),
        legend.text = element_text(size=12),
        legend.position = c(.95, .95),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.justification = c("right", "top"),
        legend.box.just = "right") +
  ylab("Total Return") +
  scale_y_continuous(name = "Total Returns",
                     breaks = seq(-0.5, 1, 0.25),
                     limits=c(-0.5, 1.05))+
  scale_color_manual(values=c('Green','Orange', 'Purple')) +
  geom_point(data=Data60, aes(x=Date, y=Folio60), size=3, color="purple")+
  geom_label(data=Data60, aes(x=Date, y=Folio60, label = paste0(100 * signif(Folio60, 4), "%")), color = "black", size=5, nudge_y = -.05) + 
  labs(title = "60-40 Portfolio 12-Month Total Returns")

```

```{r}
Monthly_Data1 = Monthly_Data1 %>%
  mutate("LC60" = Monthly_Data1$`Large Cap TR` * 0.6)

Monthly_Data1 = Monthly_Data1 %>%
  mutate("Fix40" = Monthly_Data1$FIXED * 0.4)

Monthly_Data1 = Monthly_Data1 %>%
  mutate("Portfolio" = Monthly_Data1$LC60 + Monthly_Data1$Fix40)

Monthly_Data1_LC = data.frame(matrix(nrow=12, ncol=97))
colnames(Monthly_Data1_LC) = c(seq(1926,2022,1))

Monthly_Data1_Fix = data.frame(matrix(nrow=12, ncol=97))
colnames(Monthly_Data1_Fix) = c(seq(1926,2022,1))

Monthly_Data1_Portfolio = data.frame(matrix(nrow=12, ncol=97))
colnames(Monthly_Data1_Portfolio) = c(seq(1926,2022,1))

for(i in 1:97){
  x = (i-1)*12 + 1
  y = 12 * i
  Monthly_Data1_LC[1:12, i] = Monthly_Data1$LC60[x:y]
  Monthly_Data1_Fix[1:12, i] = Monthly_Data1$Fix40[x:y]
  Monthly_Data1_Portfolio[1:12, i] = Monthly_Data1$Portfolio[x:y]}

Monthly_stats_LC = data.frame(matrix(nrow=97, ncol = 6))
Monthly_stats_Fix = data.frame(matrix(nrow=97, ncol=6))
Monthly_stats_Portfolio = data.frame(matrix(nrow=97, ncol=6))
colnames(Monthly_stats_LC) = c("year", "min", "max", "Mean", "STD_DEV", "Variance")
colnames(Monthly_stats_Fix) = c("year", "min", "max", "Mean", "STD_DEV", "Variance")
colnames(Monthly_stats_Portfolio) = c("year", "min", "max", "Mean", "STD_DEV", "Variance")
Monthly_stats_LC$year = c(1926:2022)
Monthly_stats_Fix$year = c(1926:2022)
Monthly_stats_Portfolio$year = c(1926:2022)

for(i in 1:97){
    Monthly_stats_LC[i, 2] = min(Monthly_Data1_LC[, i])
    Monthly_stats_Fix[i, 2] = min(Monthly_Data1_Fix[, i])
    Monthly_stats_Portfolio[i, 2] = min(Monthly_Data1_Portfolio[, i])
    Monthly_stats_LC[i, 3] = max(Monthly_Data1_LC[, i])
    Monthly_stats_Fix[i, 3] = max(Monthly_Data1_Fix[, i])
    Monthly_stats_Portfolio[i, 3] = max(Monthly_Data1_Portfolio[, i])
    Monthly_stats_LC[i, 4] = sum(Monthly_Data1_LC[,i])
    Monthly_stats_Fix[i, 4] = sum(Monthly_Data1_Fix[,i])
    Monthly_stats_Portfolio[i, 4] = sum(Monthly_Data1_Portfolio[,i])
    Monthly_stats_LC[i, 4] = Monthly_stats_LC[i, 4]/12
    Monthly_stats_Fix[i, 4] = Monthly_stats_Fix[i, 4]/12
    Monthly_stats_Portfolio[i, 4] = Monthly_stats_Portfolio[i, 4]/12
    Monthly_stats_LC[i, 5] = sqrt(var(Monthly_Data1_LC[, i]))
    Monthly_stats_Fix[i, 5] = sqrt(var(Monthly_Data1_Fix[, i]))
    Monthly_stats_Portfolio[i, 5] = sqrt(var(Monthly_Data1_Portfolio[, i]))
    Monthly_stats_LC[i, 6] = var(Monthly_Data1_LC[, i])
    Monthly_stats_Fix[i, 6] = var(Monthly_Data1_Fix[, i])
    Monthly_stats_Portfolio[i, 6] = var(Monthly_Data1_Portfolio[, i])}

ggplot(data = Monthly_stats_LC, aes(x = year, y = Mean,color="Large Cap")) + geom_line() +
geom_line(data = Monthly_stats_Fix, aes(x = year, y = Mean, color="Fixed")) +
geom_line(data = Monthly_stats_Portfolio, aes(x = year, y = Mean, color="Portfolio")) + xlim(1926,2022)


```

```{r}
# Fixed Statistics
Fixed_stats = data.frame(matrix(nrow=102, ncol=7))
colnames(Fixed_stats) = c("Spread", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance")
Fixed_stats$Spread = colnames(Monthly_Fixed)[2:103]
Fixed_stats$Spread_num = c(NA, seq(0,100,1))

for(i in 1:102){
    Fixed_stats[i, 3] = min(Monthly_Fixed[, i+1])
    Fixed_stats[i, 4] = max(Monthly_Fixed[, i+1])
    Fixed_stats[i, 5] = sum(Monthly_Fixed[,i+1])
    Fixed_stats[i, 5] = Fixed_stats[i, 5]/1153
    Fixed_stats[i, 6] = sqrt(var(Monthly_Fixed[, i+1]))
    Fixed_stats[i, 7] = var(Monthly_Fixed[, i+1])}

ggplot(data = Fixed_stats[2:102,], aes(x = Spread_num, y = Mean,color="red1")) + geom_line() +
geom_line(data = Fixed_stats[2:102,], aes(x = Spread_num, y = Variance, color="red2")) +
geom_line(data = Fixed_stats[2:102,], aes(x = Spread_num, y = STD_DEV, color="red3")) + ylim(0,0.2)


# Large Cap Statistics

LC_stats = data.frame(matrix(nrow=102, ncol=7))
colnames(LC_stats) = c("Spread", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance")
LC_stats$Spread = colnames(Monthly_LC)[2:103]
LC_stats$Spread_num = c(NA, seq(0,100,1))


for(i in 1:101){
    LC_stats[i, 3] = min(Monthly_LC[, i+1])
    LC_stats[i, 4] = max(Monthly_LC[, i+1])
    LC_stats[i, 5] = sum(Monthly_LC[,i+1])
    LC_stats[i, 5] = LC_stats[i, 5]/1153
    LC_stats[i, 6] = sqrt(var(Monthly_LC[, i+1]))
    LC_stats[i, 7] = var(Monthly_LC[, i+1])}

ggplot(data = LC_stats[2:102,], aes(x = Spread_num, y = Mean, color="red1")) + geom_line() +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = Variance, color="red2")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = STD_DEV, color="red3")) + ylim(0, 0.2)


# Portfolio Statistics

Portfolio_stats = data.frame(matrix(nrow=101, ncol=7))
colnames(Portfolio_stats) = c("Spread", "Spread_num", "min", "max", "Mean", "STD_DEV", "Variance")
Portfolio_stats$Spread = colnames(Monthly_Portfolio)[2:102]
Portfolio_stats$Spread_num = c(seq(0,100,1))


for(i in 1:101){
    Portfolio_stats[i, 3] = min(Monthly_Portfolio[, i+1])
    Portfolio_stats[i, 4] = max(Monthly_Portfolio[, i+1])
    Portfolio_stats[i, 5] = sum(Monthly_Portfolio[,i+1])
    Portfolio_stats[i, 5] = Portfolio_stats[i, 5]/1153
    Portfolio_stats[i, 6] = sqrt(var(Monthly_Portfolio[, i+1]))
    Portfolio_stats[i, 7] = var(Monthly_Portfolio[, i+1])}


ggplot(data = Portfolio_stats, aes(x = Spread_num, y = Mean), color="green") + geom_line() +
geom_line(data = Portfolio_stats, aes(x = Spread_num, y = Variance), color="red") +
geom_line(data = Portfolio_stats, aes(x = Spread_num, y = STD_DEV), color="blue") + ylim(0,0.2)

ggplot(data = Fixed_stats[2:102,], aes(x = Spread_num, y = Mean, color="red1")) + geom_line() +
geom_line(data = Fixed_stats[2:102,], aes(x = Spread_num, y = Variance, color="red2")) +
geom_line(data = Fixed_stats[2:102,], aes(x = Spread_num, y = STD_DEV, color="red3")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = Mean, color="blue1")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = Variance, color="blue2")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = STD_DEV, color="blue3"))

ggplot(data = Fixed_stats[2:102,], aes(x = Spread_num, y = Mean, color="red1")) + geom_line() +
geom_line(data = Fixed_stats[2:102,], aes(x = Spread_num, y = Variance, color="red2")) +
geom_line(data = Fixed_stats[2:102,], aes(x = Spread_num, y = STD_DEV, color="red3")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = Mean, color="blue1")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = Variance, color="blue2")) +
geom_line(data = LC_stats[2:102,], aes(x = Spread_num, y = STD_DEV, color="blue3")) +
geom_line(data = Portfolio_stats, aes(x = Spread_num, y = Mean, color="green1")) +
geom_line(data = Portfolio_stats, aes(x = Spread_num, y = Variance, color="green2")) +
geom_line(data = Portfolio_stats, aes(x = Spread_num, y = STD_DEV, color="green3")) + ylim(0,0.2)


```


```{r}
# Portfolio 60/40
sig_loss1 = qnorm(0.05, mean = mean(Monthly_Data$Folio60), sd = sqrt(var(Monthly_Data$Folio60)), lower.tail = TRUE)
sig_loss2 = qnorm(0.01, mean = mean(Monthly_Data$Folio60), sd = sqrt(var(Monthly_Data$Folio60)), lower.tail = TRUE)
sig_loss3 = qnorm(0.001, mean = mean(Monthly_Data$Folio60), sd = sqrt(var(Monthly_Data$Folio60)), lower.tail = TRUE)
sig_loss4 = qnorm(0.0001, mean = mean(Monthly_Data$Folio60), sd = sqrt(var(Monthly_Data$Folio60)), lower.tail = TRUE)

significant_losses = subset(Monthly_Data, Monthly_Data$Folio60 <= sig_loss1)[c("Date", "Folio60")]
require(zoo)
significant_losses["Year"] <- year(significant_losses$Date)
significant_losses["Month"] = months(significant_losses$Date)
significant_losses$Month <- factor(significant_losses$Month, levels = rev(month.name))
significant_losses$Year <- factor(significant_losses$Year, levels = unique(year(significant_losses$Date)))
significant_losses["Probability"] = NA


for(i in 1:54){
  if(significant_losses$Folio60[i] < sig_loss1){
    significant_losses$Probability[i] = "< 5%"}
  if(significant_losses$Folio60[i] < sig_loss2){
    significant_losses$Probability[i] = "< 1%"}
  if(significant_losses$Folio60[i] < sig_loss3){
    significant_losses$Probability[i] = "< 0.1%"}
  if(significant_losses$Folio60[i] < sig_loss4){
    significant_losses$Probability[i] = "< 0.01%"}}

significant_losses$Probability <- factor(significant_losses$Probability, levels = c("< 5%", "< 1%", "< 0.1%", "< 0.01%"))

significant_losses %>%
  ggplot()+
  geom_col(aes(x=abs(Folio60), y = Month, fill = Probability)) +
  scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) +
  facet_wrap(~as.character(Year)) +
  labs(title="12-Month Significant Losses on the 60/40 Portfolio",
  x = "Investment Loss")+
  scale_fill_manual(values  = c("< 5%" = "yellow",
                                "< 1%" = "orange",
                                "< 0.1%" = "orangered1",
                                "< 0.01%" = "red2")) +
  geom_text(aes(x = abs(Folio60), y = Month, label = round(abs(Folio60), 4)), hjust=1) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size = 15),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 15),
        title =element_text(size=18, face='bold'),
        legend.text = element_text(size = 12))


# Fixed
sig_Loss_FIX1 = qnorm(0.05, mean = mean(Monthly_Data$FIXED), sd = sqrt(var(Monthly_Data$FIXED)), lower.tail = TRUE)
sig_Loss_FIX2 = qnorm(0.01, mean = mean(Monthly_Data$FIXED), sd = sqrt(var(Monthly_Data$FIXED)), lower.tail = TRUE)
sig_Loss_FIX3 = qnorm(0.001, mean = mean(Monthly_Data$FIXED), sd = sqrt(var(Monthly_Data$FIXED)), lower.tail = TRUE)
sig_Loss_FIX4 = qnorm(0.0001, mean = mean(Monthly_Data$FIXED), sd = sqrt(var(Monthly_Data$FIXED)), lower.tail = TRUE)

significant_Losses_FIX = subset(Monthly_Data, Monthly_Data$FIXED <= sig_Loss_FIX1)[c("Date", "FIXED")]
require(zoo)
significant_Losses_FIX["Year"] <- year(significant_Losses_FIX$Date)
significant_Losses_FIX["Month"] = months(significant_Losses_FIX$Date)
significant_Losses_FIX$Month <- factor(significant_Losses_FIX$Month, levels = rev(month.name))
significant_Losses_FIX$Year <- factor(significant_Losses_FIX$Year, levels = unique(year(significant_Losses_FIX$Date)))
significant_Losses_FIX["Probability"] = NA

for(i in 1:22){
  if(significant_Losses_FIX$FIXED[i] < sig_Loss_FIX1){
    significant_Losses_FIX$Probability[i] = "< 5%"}
  if(significant_Losses_FIX$FIXED[i] < sig_Loss_FIX2){
    significant_Losses_FIX$Probability[i] = "< 1%"}
  if(significant_Losses_FIX$FIXED[i] < sig_Loss_FIX3){
    significant_Losses_FIX$Probability[i] = "< 0.1%"}
  if(significant_Losses_FIX$FIXED[i] < sig_Loss_FIX4){
    significant_Losses_FIX$Probability[i] = "< 0.01%"}}

significant_Losses_FIX$Probability <- factor(significant_Losses_FIX$Probability, levels = c("< 5%", "< 1%", "< 0.1%", "< 0.01%"))

significant_Losses_FIX %>%
  ggplot()+
  geom_col(aes(x=abs(FIXED), y = Month, fill = Probability)) +
  scale_x_continuous(breaks = c(0, 0.05, 0.10, 0.15)) +
  facet_wrap(~as.character(Year)) +
  labs(title="12-Month Significant Losses on the Blended Fixed Income Fund",
  x = "Investment Loss")+
  scale_fill_manual(values  = c("< 5%" = "yellow",
                                "< 1%" = "orange",
                                "< 0.1%" = "orangered1")) +
  geom_text(aes(x = abs(FIXED), y = Month, label = round(abs(FIXED), 4)), hjust=1) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size = 15),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 15),
        title =element_text(size=18, face='bold'),
        legend.text = element_text(size = 12))


# Fixed 60/40
sig_Loss_FIX1a = qnorm(0.05, mean = mean(Monthly_Data$FIX60), sd = sqrt(var(Monthly_Data$FIX60)), lower.tail = TRUE)
sig_Loss_FIX2a = qnorm(0.01, mean = mean(Monthly_Data$FIX60), sd = sqrt(var(Monthly_Data$FIX60)), lower.tail = TRUE)
sig_Loss_FIX3a = qnorm(0.001, mean = mean(Monthly_Data$FIX60), sd = sqrt(var(Monthly_Data$FIX60)), lower.tail = TRUE)
sig_Loss_FIX4a = qnorm(0.0001, mean = mean(Monthly_Data$FIX60), sd = sqrt(var(Monthly_Data$FIX60)), lower.tail = TRUE)

significant_Losses_FIXa = subset(Monthly_Data, Monthly_Data$FIX60 <= sig_Loss_FIX1a)[c("Date", "FIX60")]
require(zoo)
significant_Losses_FIXa["Year"] <- year(significant_Losses_FIXa$Date)
significant_Losses_FIXa["Month"] = months(significant_Losses_FIXa$Date)
significant_Losses_FIXa$Month <- factor(significant_Losses_FIXa$Month, levels = rev(month.name))
significant_Losses_FIXa$Year <- factor(significant_Losses_FIXa$Year, levels = unique(year(significant_Losses_FIXa$Date)))
significant_Losses_FIXa["Probability"] = NA

for(i in 1:22){
  if(significant_Losses_FIXa$FIX60[i] < sig_Loss_FIX1a){
    significant_Losses_FIXa$Probability[i] = "< 5%"}
  if(significant_Losses_FIXa$FIX60[i] < sig_Loss_FIX2a){
    significant_Losses_FIXa$Probability[i] = "< 1%"}
  if(significant_Losses_FIXa$FIX60[i] < sig_Loss_FIX3a){
    significant_Losses_FIXa$Probability[i] = "< 0.1%"}
  if(significant_Losses_FIXa$FIX60[i] < sig_Loss_FIX4a){
    significant_Losses_FIXa$Probability[i] = "< 0.01%"}}

significant_Losses_FIXa$Probability <- factor(significant_Losses_FIXa$Probability, levels = c("< 5%", "< 1%", "< 0.1%", "< 0.01%"))

significant_Losses_FIXa %>%
  ggplot()+
  geom_col(aes(x=abs(FIX60), y = Month, fill = Probability)) +
  facet_wrap(~as.character(Year)) +
  labs(title="12-Month Significant Losses on the Blended Fixed Income Fund for the 60/40 Portfolio",
  x = "Investment Loss")+
  scale_fill_manual(values  = c("< 5%" = "yellow",
                                "< 1%" = "orange",
                                "< 0.1%" = "orangered1")) +
  geom_text(aes(x = abs(FIX60), y = Month, label = round(abs(FIX60), 4)), hjust=1) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size = 15),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 15),
        title =element_text(size=18, face='bold'),
        legend.text = element_text(size = 12))


# Large Cap
sig_Loss_LC1 = qnorm(0.05, mean = mean(Monthly_Data$`Large Cap TR`), sd = sqrt(var(Monthly_Data$`Large Cap TR`)), lower.tail = TRUE)
sig_Loss_LC2 = qnorm(0.01, mean = mean(Monthly_Data$`Large Cap TR`), sd = sqrt(var(Monthly_Data$`Large Cap TR`)), lower.tail = TRUE)
sig_Loss_LC3 = qnorm(0.001, mean = mean(Monthly_Data$`Large Cap TR`), sd = sqrt(var(Monthly_Data$`Large Cap TR`)), lower.tail = TRUE)
sig_Loss_LC4 = qnorm(0.0001, mean = mean(Monthly_Data$`Large Cap TR`), sd = sqrt(var(Monthly_Data$`Large Cap TR`)), lower.tail = TRUE)

significant_Losses_LC = subset(Monthly_Data, Monthly_Data$`Large Cap TR` <= sig_Loss_LC1)[c("Date", "Large Cap TR")]
require(zoo)
significant_Losses_LC["Year"] <- year(significant_Losses_LC$Date)
significant_Losses_LC["Month"] = months(significant_Losses_LC$Date)
significant_Losses_LC$Month <- factor(significant_Losses_LC$Month, levels = rev(month.name))
significant_Losses_LC$Year <- factor(significant_Losses_LC$Year, levels = unique(year(significant_Losses_LC$Date)))
significant_Losses_LC["Probability"] = NA

for(i in 1:60){
  if(significant_Losses_LC$`Large Cap TR`[i] < sig_Loss_LC1){
    significant_Losses_LC$Probability[i] = "< 5%"}
  if(significant_Losses_LC$`Large Cap TR`[i] < sig_Loss_LC2){
    significant_Losses_LC$Probability[i] = "< 1%"}
  if(significant_Losses_LC$`Large Cap TR`[i] < sig_Loss_LC3){
    significant_Losses_LC$Probability[i] = "< 0.1%"}
  if(significant_Losses_LC$`Large Cap TR`[i] < sig_Loss_LC4){
    significant_Losses_LC$Probability[i] = "< 0.01%"}}

significant_Losses_LC$Probability <- factor(significant_Losses_LC$Probability, levels = c("< 5%", "< 1%", "< 0.1%", "< 0.01%"))

significant_Losses_LC %>%
  ggplot()+
  geom_col(aes(x=abs(`Large Cap TR`), y = Month, fill = Probability)) +
  scale_x_continuous(breaks = c(0, 0.15, 0.30, 0.45, 0.60, 0.75)) +
  facet_wrap(~as.character(Year)) +
  labs(title="12-Month Significant Losses on Large Cap Equities",
  x = "Investment Loss")+
  scale_fill_manual(values  = c("< 5%" = "yellow",
                                "< 1%" = "orange",
                                "< 0.1%" = "orangered1",
                                "< 0.01%" = "red2")) +
  geom_text(aes(x = abs(`Large Cap TR`), y = Month, label = round(abs(`Large Cap TR`), 4)), hjust=1) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size = 15),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 15),
        title =element_text(size=18, face='bold'),
        legend.text = element_text(size = 12))


# Large Cap 60/40
sig_Loss_LC1a = qnorm(0.05, mean = mean(Monthly_Data$LC60), sd = sqrt(var(Monthly_Data$LC60)), lower.tail = TRUE)
sig_Loss_LC2a = qnorm(0.01, mean = mean(Monthly_Data$LC60), sd = sqrt(var(Monthly_Data$LC60)), lower.tail = TRUE)
sig_Loss_LC3a = qnorm(0.001, mean = mean(Monthly_Data$LC60), sd = sqrt(var(Monthly_Data$LC60)), lower.tail = TRUE)
sig_Loss_LC4a = qnorm(0.0001, mean = mean(Monthly_Data$LC60), sd = sqrt(var(Monthly_Data$LC60)), lower.tail = TRUE)

significant_Losses_LCa = subset(Monthly_Data, Monthly_Data$LC60 <= sig_Loss_LC1a)[c("Date", "LC60")]
require(zoo)
significant_Losses_LCa["Year"] <- year(significant_Losses_LCa$Date)
significant_Losses_LCa["Month"] = months(significant_Losses_LCa$Date)
significant_Losses_LCa$Month <- factor(significant_Losses_LCa$Month, levels = rev(month.name))
significant_Losses_LCa$Year <- factor(significant_Losses_LCa$Year, levels = unique(year(significant_Losses_LCa$Date)))
significant_Losses_LCa["Probability"] = NA

for(i in 1:60){
  if(significant_Losses_LCa$LC60[i] < sig_Loss_LC1a){
    significant_Losses_LCa$Probability[i] = "< 5%"}
  if(significant_Losses_LCa$LC60[i] < sig_Loss_LC2a){
    significant_Losses_LCa$Probability[i] = "< 1%"}
  if(significant_Losses_LCa$LC60[i] < sig_Loss_LC3a){
    significant_Losses_LCa$Probability[i] = "< 0.1%"}
  if(significant_Losses_LCa$LC60[i] < sig_Loss_LC4a){
    significant_Losses_LCa$Probability[i] = "< 0.01%"}}

significant_Losses_LCa$Probability <- factor(significant_Losses_LCa$Probability, levels = c("< 5%", "< 1%", "< 0.1%", "< 0.01%"))

significant_Losses_LCa %>%
  ggplot()+
  geom_col(aes(x=abs(LC60), y = Month, fill = Probability)) +
  scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5)) +
  facet_wrap(~as.character(Year)) +
  labs(title="12-Month Significant Losses on Large Cap Equities for the 60/40 Portfolio",
  x = "Investment Loss")+
  scale_fill_manual(values  = c("< 5%" = "yellow",
                                "< 1%" = "orange",
                                "< 0.1%" = "orangered1",
                                "< 0.01%" = "red2")) +
  geom_text(aes(x = abs(LC60), y = Month, label = round(abs(LC60), 4)), hjust=1) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.text = element_text(size = 15),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 15),
        title =element_text(size=18, face='bold'),
        legend.text = element_text(size = 12))
```





```{r}
# Annual Significant 60/40 Portfolio Losses
annual_sig_Loss1 = qnorm(0.05, mean = mean(annual$Folio60), sd = sqrt(var(annual$Folio60)), lower.tail = TRUE)
annual_significant_losses = subset(annual, annual$Folio60 <= annual_sig_Loss1)[c("Date", "Folio60")]
colnames(annual_significant_losses)[1:2] = c("Year", "Total Return")
annual_significant_losses = annual_significant_losses %>%
  mutate("Probability" = paste0(100 * signif(pnorm(annual_significant_losses$`Total Return`, mean = mean(annual$Folio60), sd = sqrt(var(annual$Folio60)), lower.tail = TRUE), 4), "%"))
annual_significant_losses


# Annual Significant FIXED Losses
annual_sig_Loss_FIX1 = qnorm(0.05, mean = mean(annual$FIXED), sd = sqrt(var(annual$FIXED)), lower.tail = TRUE)
annual_significant_Losses_FIX = subset(annual, annual$FIXED <= annual_sig_Loss_FIX1)[c("Date", "FIXED")]
colnames(annual_significant_Losses_FIX)[1:2] = c("Year", "Total Return")
annual_significant_Losses_FIX = annual_significant_Losses_FIX %>%
  mutate("Probability" = paste0(100 * signif(pnorm(annual_significant_Losses_FIX$`Total Return`, mean = mean(annual$Folio60), sd = sqrt(var(annual$Folio60)), lower.tail = TRUE), 4), "%"))
annual_sig_Loss_FIX1


# Annual Significant Large Cap Losses                
annual_sig_Loss_LC1 = qnorm(0.05, mean = mean(annual$`Large Cap TR`), sd = sqrt(var(annual$`Large Cap TR`)), lower.tail = TRUE)
annual_significant_losses_LC = subset(annual, annual$`Large Cap TR` <= annual_sig_Loss_LC1)[c("Date", "Large Cap TR")]
colnames(annual_significant_losses_LC)[1:2] = c("Year", "Total Return")
annual_significant_losses_LC = annual_significant_losses_LC %>%
  mutate("Probability" = paste0(100 * signif(pnorm(annual_significant_losses_LC$`Total Return`, mean = mean(annual$`Large Cap TR`), sd = sqrt(var(annual$`Large Cap TR`)), lower.tail = TRUE), 4), "%"))
annual_significant_losses_LC
```



```{r}
Annual60 = subset(Monthly, months(Monthly$Date) == "January")[c("Date", "Alpha60")]
colnames(Annual60) = c("Date", "TR")

Monthly60 = Monthly[c("Date", "Alpha60")]
colnames(Monthly60) = c("Date", "TR")


for(i in 1:1153){
  if(Monthly60$Alpha60[i] < -0.225){
    Monthly60$line_color[i] = "red"}
  if(Monthly60$Alpha60[i] > -0.225 & Monthly60$Alpha60[i] < -0.075){
    Monthly60$line_color[i] = "redorange"}
  if(Monthly60$Alpha60[i] > -0.075 & Monthly60$Alpha60[i] < 0.075){
    Monthly60$line_color[i] = "orange"}
  if(Monthly60$Alpha60[i] > 0.075 & Monthly60$Alpha60[i] < 0.225){
    Monthly60$line_color[i] = "yelloworange"}
  if(Monthly60$Alpha60[i] > 0.225 & Monthly60$Alpha60[i] < 0.3){
    Monthly60$line_color[i] = "yellow"}
  if(Monthly60$Alpha60[i] > 0.3){
    Monthly60$line_color[i] = "green"}}

Annual60 <- Annual60 %>%
  mutate("Date" = year(Annual60$Date))



line_color <- as.factor(c("1", "2", "3", "4", "5", "6", "7"))
TR = Annual60$TR
line_color[TR < -0.2] <- 1
line_color[TR > -0.2 & TR < -0.1] <- 2
line_color[TR > -0.1 & TR < 0] <- 3
line_color[TR > 0 & TR < 0.1] <- 4
line_color[TR > 0.1 & TR < 0.2] <- 5
line_color[TR > 0.2 & TR < 0.3] <- 6
line_color[TR > 0.3] <- 7
Annual60["line_color"] <- line_color


for(i in 1:97){
  if(Annual60$Alpha60[i] < -0.2){
    Annual60$line_color[i] = "red4"}
  if(Annual60$Alpha60[i] > -0.2 & Annual60$Alpha60[i] < -0.1){
    Annual60$line_color[i] = "redorange"}
  if(Annual60$Alpha60[i] > -0.1 & Annual60$Alpha60[i] < 0){
    Annual60$line_color[i] = "orange"}
  if(Annual60$Alpha60[i] > 0 & Annual60$Alpha60[i] < 0.1){
    Annual60$line_color[i] = "goldenrod1"}
  if(Annual60$Alpha60[i] > 0.1 & Annual60$Alpha60[i] < 0.2){
    Annual60$line_color[i] = "yellow"}
  if(Annual60$Alpha60[i] > 0.2 & Annual60$Alpha60[i] < 0.3){
    Annual60$line_color[i] = "greenyellow"}
  if(Annual60$Alpha60[i] > 0.3){
    Annual60$line_color[i] = "green"}}

library(lubridate)

ggplot2::ggplot(data = Annual60, aes(x=Date, y = Alpha60, color = line_color)) + geom_line(aes(group = 1)) + geom_point(data = Annual60, aes(x=Date, y = Alpha60, color = line_color)) + ylim(-0.3, 0.4)

Annual60 <- Annual60 %>%
  mutate(line_color = c(factor(Annual60$line_color)))


ggplot(data = Annual60, aes(x=Date, y = Alpha60, color = line_color)) + geom_line(data = Annual60, aes(color = c(Alpha60 < -0.225, Alpha60 > -0.225 & Alpha60 < -0.075)))+ geom_point(data = Annual60, aes(color = c(Alpha60 < -0.225, Alpha60 > -0.225 & Alpha60 < -0.075))) + ylim(-0.3, 0.4)

plot(x=Annual60$Date, y=Annual60$Alpha60, col = Annual60$line_color)



myPlot = function(y, x,
    colors=c("blue","red"),
    xlab=deparse(substitute(x)),
    ylab=deparse(substitute(y)), ...)
{
    n = length(x)
    y.pos = y.neg = y
    y.pos[y<0] = 0
    y.neg[y>0] = 0
    plot(y~x, type="n", xlab=xlab, ylab=ylab, ...)
    grid()
    polygon(c(x[1],x,x[n]),c(0,y.pos,0),col=colors[1],border=NA)
    polygon(c(x[1],x,x[n]),c(0,y.neg,0),col=colors[2],border=NA)}

myPlot(x = Annual60$Date, y = Annual60$Alpha60)

ggplot2::ggplot(data = Annual60, aes(x=Date, y = Alpha60, color = line_color)) + geom_line(aes(group = 1)) + geom_point(data = Annual60, aes(x=Date, y = Alpha60, color = line_color)) + ylim(-0.3, 0.4)

A = 
plot(A~y2, data, type="h", lwd=2, col=c("blue","red")[1+(A<0)],xlab="Year")


install.packages("RColorBrewer")
library(RColorBrewer)
my_colors = brewer.pal(7, "Set2") 

clplot(x=(Monthly$Date), y=Monthly$Alpha60, main="", lwd=1, levels=c(-0.3, -0.15, 0, 0.15, 0.30, 0.45, 0.6), col=my_colors, showcuts=T , bty="n", ylim=c(-0.5,0.6))

my_colors = c("red4", "orangered2", "yellow", "green", "blue")
clplot(x=Annual60$Date, y=Annual60$Alpha60, main="", lwd=1, levels=c(-0.225, -0.075, 0.075, 0.225, 0.30), col=my_colors, showcuts=F , bty="n", ylim=c(-0.3,0.4), xlim = c(1925, 2025), xlab="Year", ylab="Total Return", title(main = "Annual 60/40 Total Returns"))


for(i in 0:100){
  alpha = i/100
  for(j in 1:1153){
    Monthly[j,i+4]= alpha*Monthly$LCTR[j] + (1-alpha)*Monthly$FIXED_TR[j]}}

plot(xlab= "Alpha", x = 0:10 0, ylab="Total Return", y= Monthly[1153, 4:104], main = "All 2022 Total Returns", par(lty = 1))
```

```{r}
Alpha = data.frame(matrix(nrow=101, ncol=6))
colnames(Alpha) = c("Spread_Ratio", "min", "max", "Mean", "STD_DEV", "Std_29") 
Alpha$Spread_Ratio = colnames(data)[4:104]

for(i in 1:length(Alpha$Spread_Ratio)){
    Alpha[i, 2] = min(data[, i+3])
    Alpha[i, 3] = max(data[, i+3])
    Alpha[i, 4] = sum(data[,i+3])
    Alpha[i, 4] = Alpha[i, 4]/97
    Alpha[i, 5] = sqrt(var(data[, i+3]))
    Alpha[i, 6] = sqrt(var(data[29:97, i+3]))}


Returns_30yr = c(2.755,
2.954166667,
3.0975,
3.443333333,
3.4825,
4.078333333,
4.119166667,
3.941666667,
4.055,
4.073333333,
4.186666667,
4.223333333,
4.694166667,
4.9,
5.345833333,
6.1725,
6.734166667,
5.998333333,
5.796666667,
6.9875,
7.983333333,
8.213333333,
7.944166667,
7.725,
8.544166667,
9.316666667,
11.43333333,
13.56333333,
12.66333333,
11.25583333,
12.43333333,
10.70333333,
7.69,
8.609166667,
8.936666667,
8.401666667,
8.619166667,
8.085,
7.675,
6.579166667,
7.409166667,
6.8075,
6.723333333,
6.5675,
5.531666667,
5.913333333,
5.88,
5.4675,
5.405833333,
5.0325,
5.1,
4.520833333,
4.873333333,
4.796666667,
4.218333333,
4.095,
4.180833333,
3.884166667,
2.8825,
3.459166667,
3.269166667,
2.818333333,
2.58,
2.886666667,
3.095,
2.525,
1.51,
2.0475,
3.161666667
)

Returns_30yr=Returns_30yr/100

x = 1954:2022

frame = data.frame(matrix(ncol=102, nrow=69))
frame[,1] = c(seq(1954,2022))
for(i in 4:104){
  for(j in 29:97){
    z = data[j,i] - Returns_30yr[j-28]
    frame[j-28, i-2] = z/Alpha$Std_29[i-3]}}

  

vect = vector()
for(i in 2:102){
  vect = append(vect, mean(frame[, i]))}


plot(x = 0:100, y = vect, main = "Historic Sharpe Ratio", ylab="Sharpe Ratio", xlab="alpha", type = "l")

# Conditional Expectation of total return given it will be positive
Alpha["E[TR | TR > 0]"]=NA

for(i in 4:104){
  y = data.frame(data[,c(1,i)])
  y = y %>% arrange(y[,2])
  colnames(y) = c(paste0("Date",i-4), paste0(i-4, "/", 104-i))
  y = subset(y, y[,2] > 0)
  Alpha$`E[TR | TR > 0]`[i-3] = mean(y[,2])}


Alpha["E[TR | TR < 0]"]=NA

for(i in 4:104){
  y = data.frame(data[,c(1,i)])
  y = y %>% arrange(y[,2])
  colnames(y) = c(paste0("Date",i-4), paste0(i-4, "/", 104-i))
  y = subset(y, y[,2] < 0)
  Alpha$`E[TR | TR < 0]`[i-3] = mean(y[,2])}


for(i in 4:104){
  y = data.frame(data[,c(1,i)])
  y = y %>% arrange(y[,2])
  colnames(y) = c(paste0("Date",i-4), paste0(i-4, "/", 104-i))
  y = subset(y, y[,2] > 0)
  Alpha$`SD[TR | TR > 0]`[i-3] = sqrt(var(y[,2]))}

for(i in 4:104){
  y = data.frame(data[,c(1,i)])
  y = y %>% arrange(y[,2])
  colnames(y) = c(paste0("Date",i-4), paste0(i-4, "/", 104-i))
  y = subset(y, y[,2] < 0)
  Alpha$`SD[TR | TR < 0]`[i-3] = sqrt(var(y[,2]))}

  
library("plotrix")

Alpha = Alpha %>%
  mutate("Z-Score" = (0 - Alpha$Mean)/Alpha$STD_DEV)

Alpha = Alpha %>%
  mutate("P(TR > 0)" = pnorm(Alpha$`Z-Score`, lower.tail = FALSE))

Alpha = Alpha %>%
  mutate("Z-Score2" = (-0.16 - Alpha$Mean)/Alpha$STD_DEV)

Alpha = Alpha %>%
  mutate("P(TR > -0.16)" = pnorm(Alpha$`Z-Score2`, lower.tail = FALSE))

x = (Alpha$`P(TR > -0.16)`[82] - 0.95)
y = x/Alpha$`P(TR > -0.16)`[83]
y

plot(x = 0:100, y = Alpha$`P(TR > 0)`, type = "l")

plot(x = 0:100, y = Alpha$`P(TR > -0.16)`, type = "l")
abline(h=0.95, col="red")

qnorm(0.95, lower.tail = TRUE)

Alpha["E[TR]"]=NA
for(i in 1:101){
  Alpha$`E[TR]` = (Alpha$`P(TR > 0)`[i] * Alpha$`E[TR | TR > 0]`[i]) + ((1 - Alpha$`P(TR > 0)`[i]) * Alpha$`E[TR | TR < 0]`[i])}

plot(x = 0:100, y = Alpha$`P(TR > 0)`, xlab="Alpha(Large Cap %)", ylab="Probability", main = "Probability Total Returns are Positive")




weighted_TR <- read_excel("Pension Investment Calculation (Annual) MRP600 Sim.xlsx", 
    sheet = "Weighted TR", col_names = FALSE)
vect0 = vector()
for(i in 1:length(colnames(weighted_TR))){
  for(j in 1:length(weighted_TR$...1)){
    vect0 = append(vect0, weighted_TR[j,i])
  }
}
sum = 0
for(i in 1:30000){
  sum = sum + vect0[[i]]}
mean = sum/30000
mean
list1 = list(rep(NA, 30000))
for(i in 1:30000){
  list1[i] = vect0[[i]]}

list1 = data.frame(list1)
list1 = data.frame(t(list1))

sum1 = sum(list1$t.list1.[1:10000])
mean1 = sum1/10000
sd1 = sqrt(var(list1$t.list1.[1:10000]))
diff1 = -0.16-mean1
z_score1 = diff1/sd1
pnorm(z_score1, lower.tail=TRUE)

sd = sqrt(var(list1$t.list1.))
diff = -0.16 - mean 
z_score = diff/sd
pnorm(z_score, lower.tail=TRUE)


Conf = Alpha[c(1,4,5,7:10,12:13)]
Conf = Conf %>%
  mutate("+lower" = Conf$`E[TR | TR > 0]` - 1.96*Conf$`SD[TR | TR > 0]`)

Conf = Conf %>%
  mutate("+upper" = Conf$`E[TR | TR > 0]` + 1.96*Conf$`SD[TR | TR > 0]`)


plotCI(x = 0:100, y = Conf$`E[TR | TR > 0]`, li = Conf$`+lower`, ui = Conf$`+upper`, main="CI Assuming TR > 0", ylab="Total Return", xlab="alpha")
abline(v = 59, col = "red", lty = "dashed")
abline(h = max(Conf$`+lower`), col = "red", lty = "dashed")
mtext("max(lower bound) @ 59", side=3, line = -1, adj = 0.1, cex=.7)

library(ggplot2)

df = data.frame(matrix(ncol=3, nrow=9797))
for(i in 0:100){
  x = i*97 + 1
  y = (1+i)*97
  df[x:y, 1] = data[,i+4]
  df[x:y, 2] = paste0(colnames(data)[i+4])}

Alpha[c("Spread_Ratio", "min", "max")][97:101,]

ggplot2::ggplot(data = df[1:1552,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.025)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.15, 0.35, 0.1),
                     limits=c(-0.15, 0.35)) +
  scale_y_continuous(name = "Frequency") +
  ggtitle("Histograms w/ Varying Alpha") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=10),
        strip.background = element_rect())

ggplot2::ggplot(data = df[1553:3104,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.025)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.15, 0.35, 0.1),
                     limits=c(-0.15, 0.35)) +
  scale_y_continuous(name = "Frequency") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=10),
        strip.background = element_rect())


ggplot2::ggplot(data = df[3105:4656,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.025)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.25, 0.35, 0.1),
                     limits=c(-0.25, 0.35)) +
  scale_y_continuous(name = "Frequency") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=9),
        strip.background = element_rect())

ggplot2::ggplot(data = df[4657:6208,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.025)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.3, 0.4, 0.15),
                     limits=c(-0.3, 0.4)) +
  scale_y_continuous(name = "Frequency") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=10),
        strip.background = element_rect())

ggplot2::ggplot(data = df[6209:7760,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.025)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.35, 0.45, 0.15),
                     limits=c(-0.35, 0.45)) +
  scale_y_continuous(name = "Frequency") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=10),
        strip.background = element_rect())

ggplot2::ggplot(data = df[7761:9312,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.05)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.45, 0.55, 0.2),
                     limits=c(-0.45, 0.55)) +
  scale_y_continuous(name = "Frequency") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=10),
        strip.background = element_rect())

ggplot2::ggplot(data = df[9313:9797,], mapping = aes(x=X1), freq=FALSE) + 
  geom_histogram(binwidth=0.05)+
  geom_density(col="red") +
  scale_x_continuous(name = "Total Returns",
                     breaks = seq(-0.45, 0.55, 0.2),
                     limits=c(-0.45, 0.55)) +
  scale_y_continuous(name = "Frequency") +
  scale_fill_gradient("Count", low = "blue", high = "red") +
  geom_vline(aes(xintercept = mean(df$X1), group = X2), size = 1, colour = "#FF3721",
                   linetype = "dashed") +
  facet_wrap(~X2) + 
  geom_line(aes(y = mean(df$X1)))+
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size=10),
        strip.background = element_rect())




```




```{r}
library(readxl)
data2 <- read_excel("Project 2 Historical Data.xlsx", 
    range = "A1186:P1283")

colnames(data2) = c("Year",	"Ibbotson® SBBI® US Large-Cap Stocks (Total Return)", "Ibbotson® SBBI® US Large-Cap Stocks (Income Return)",	"Ibbotson® SBBI® US Large-Cap Stocks (Capital Appreciation  Return)",	"Ibbotson® SBBI® US Small-Cap Stocks (Total Return)",	"Ibbotson® SBBI® US Long-term (20-Year) Corporate Bonds (Total Return)",	"Ibbotson® SBBI® US Long-term (20-Year) Government Bonds (Total Return)",	"Ibbotson® SBBI® US Long-term (20-Year) Government Bonds (Income Return)",	"Ibbotson® SBBI® US Long-term (20-Year) Government Bonds (Capital Appreciation Return)",	"Ibbotson® SBBI® US Long-term (20-Year)  Government Bonds (Yield)",	"Ibbotson® SBBI® US Intermediate-term (5-Year) Government Bonds (Total Return)",	"Ibbotson® SBBI® US Intermediate-term (5-Year) Government Bonds (Income Return)",	"Ibbotson® SBBI® US Intermediate-term (5-Year) Government Bonds (Capital Appreciation Return)",	"Ibbotson® SBBI® US Intermediate-term (5-Year) Government Bonds (Yield)",	"Ibbotson® SBBI® US (30-Day) Treasury Bills",	"Ibbotson® SBBI® US Inflation")

data2 = data2[, c(1,2,6,7,11)]

data2["Large_Cap"] = NA
for(i in 1:97){
  data2$Large_Cap[i] = data2$`Ibbotson® SBBI® US Large-Cap Stocks (Total Return)`[i] + data2$`Ibbotson® SBBI® US Long-term (20-Year) Government Bonds (Total Return)`[i]
}
  
data2 = data2 %>%
  mutate("Large_Cap" =data2[,2]+data2[,4])


Conf2 = data.frame(matrix(nrow=97, ncol=102))
colnames(Conf2) = c("Year", colnames(data)[4:104])





for(i in 0:100){
  alpha = i
  alpha=alpha/100
  for(j in 1:97){
    long_corp = (1-alpha) * 0.35 * data2$`Ibbotson® SBBI® US Long-term (20-Year) Corporate Bonds (Total Return)`[j]
    intermediate_gov = (1-alpha) * 0.65 * data2$`Ibbotson® SBBI® US Intermediate-term (5-Year) Government Bonds (Total Return)`[j]
    Large_Cap = alpha * data2$`Ibbotson® SBBI® US Large-Cap Stocks (Total Return)`[j]
    TR = long_corp+intermediate_gov+Large_Cap
    Conf2[j, i+2] = TR}}
Conf2$Year = data2$Year


vect2 = vector()
for(i in 2:102){
  vect2 = append(vect2, mean(Conf2[,i]))}
plot(x=0:100, y = vect2)



data3 = data.frame(matrix(nrow=70, ncol=102))
colnames(data3) = c("Year", colnames(data)[4:104])
data3$Year[1:68] = data$Date[1:68]
data3$Year[69] = "mean(Interest Compounded Annually)"
data3$Year[70] = "sd(Interest Compounded Annually)"
for(i in 4:104){
  for(j in 1:68){
    prod = 1
    y = j+29
    x = data[j:y, i]
    x = x + 1
    for(k in 1:30){
      prod = prod * x[k,1]}
  data3[j,i-2] = prod^(1/30)-1}}

for(i in 2:102){
  x = data3[,i][1:68]
  sum = 0
  for(j in 1:length(x)){
    sum = sum + x[j]}
  mean = sum/68
    data3[69, i] = mean
    data3[70, i] = sqrt(var(x))}

Sharpe_Ratio = data.frame(matrix(nrow=101, ncol = 2))
colnames(Sharpe_Ratio) = c("Alpha", "Sharpe_Ratio")
Sharpe_Ratio[,1] = colnames(data3)[2:102]
for(i in 0:100){
  diff = data3[69, i+2] - .05
  ratio = diff/data3[70, i+2]
  Sharpe_Ratio[i+1, 2] = ratio}




```


